---
title: "Analysis of sample of 110 closed pull requests"
csl: "ieee.csl"
bibliography: "mergedprs-analysis.bib"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

\newpage

```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(dplyr)
library(ggplot2)
library(grid)
library(scales)
library(pander)

summ <- read.csv("data/allSummary.csv.gz")
```

```{r, echo=FALSE, eval=FALSE}
set.seed(1334532099)
pullRequestSampleForMergedInspection <- sample_n(summ, 200)
write.csv(pullRequestSampleForMergedInspection, "mergedprs-analysis-sample.csv")
```

```{r, echo=FALSE}
summ <- read.csv("mergedprs-analysis-sample.csv")
pullRequests <- select(summ, projectName, pullRequestId)
partitions <- read.csv("data/allPartitions.csv.gz")
partitions <- partitions %>%
  semi_join(summ, by=c("projectName", "pullRequestId"))

# Adds diffsInNonTrivialPartitions and RDN column to summ
diffsInNonTrivialPartitions <- pullRequests %>%
  left_join(filter(partitions, isTrivial == "false"), by=c("projectName", "pullRequestId")) %>%
  group_by(projectName, pullRequestId) %>%
  summarise(diffsInNonTrivialPartitions = sum(!is.na(isTrivial)))
summ <- summ %>%
  inner_join(diffsInNonTrivialPartitions, by=c("projectName", "pullRequestId")) %>%
  mutate(rdn = diffsInNonTrivialPartitions / diffs)

# Adds diffsInTrivialPartitions and RDN column to summ
summ <- summ %>%
  mutate(diffsInTrivialPartitions = diffs - diffsInNonTrivialPartitions) %>%
  mutate(rdt = diffsInTrivialPartitions / diffs)

# Remove pull requests without diffs
summ <- filter(summ, diffs >= 1)
```

# Research Question

* RQ1: Can we predict whether a pull request is merged (accepted) based on the number of partitions returned by JClusterChanges?

Intuitively, we expect to observe an inverse correlation between the number of non-trivial partitions and the probability of the pull request being merged. That is, we expect that pull requests with multiple non-trivial partitions will have a low acceptance rate because they likely contain independent modifications and are consequently hard to understand and poorly organized.

# Dataset

We manually inspected 110 closed pull requests selected at random from the most popular projects in GitHub and, for each of them, we determined: 

* if it was merged (accepted);
* if its status on GitHub is set to "merged"";
* the cause for rejection if it was not merged.

This dataset can be downloaded at: https://github.com/victorclf/ccjava-analysis/blob/master/mergedprs-analysis-sample.csv

For this analysis, we removed pull requests that did not have any diff-regions and ended up with 101 closed pull requests for the analysis. Some pull requests do not have any diff-regions because ccjava does not consider code deletions and diff-regions which contain only comments, import statements, package declarations, blank characters and empty lines.

```{r, echo=FALSE}
numPrs <- count(summ)$n
numMergedPrs <- count(filter(summ, merged == "true"))$n
numNonMergedPrs <- count(filter(summ, merged == "false"))$n
```

| Merged  |  Count  |  Proportion  |
|:----:|:----:|:-----:|
|  Yes   |  `r numMergedPrs`   |   `r percent(numMergedPrs / numPrs)`   |
|  No    |  `r numNonMergedPrs` |   `r percent(numNonMergedPrs / numPrs)`   |

Table: Summary of the dataset.


# RQ1: Can we predict whether a pull request is merged (accepted) based on the number of partitions returned by ccjava?

## Non-Trivial Partitions
```{r, echo=FALSE, eval=FALSE}
count(filter(summ, nonTrivialPartitions == 0, merged == "true")) / count(filter(summ, merged == "true"))
```

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=1) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request") +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_dodge(), col="black", binwidth=1) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request (dodge)") +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_stack(), col="black", binwidth=1) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request (stack)") +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=1) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request (fill)") +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=merged, y=nonTrivialPartitions)) +
  geom_boxplot() +
  ggtitle("Boxplot of Non-Trivial Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Non-Trivial Partitions")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, color=merged)) +
  geom_density() +
  ggtitle("Density Plot of Non-Trivial Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Non-Trivial Partitions")
```

## Trivial Partitions
```{r, echo=FALSE}
ggplot(summ, aes(x=trivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=1) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Histogram of Trivial Partitions in a Pull Request") +
  xlab("Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=trivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_dodge(), col="black", binwidth=1) +
  ggtitle("Histogram of Trivial Partitions in a Pull Request (dodge)") +
  xlab("Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=trivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_stack(), col="black", binwidth=1) +
  ggtitle("Histogram of Trivial Partitions in a Pull Request (stack)") +
  xlab("Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=trivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=1) +
  ggtitle("Histogram of Trivial Partitions in a Pull Request (fill)") +
  xlab("Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=merged, y=trivialPartitions)) + 
  geom_boxplot() +
  ggtitle("Boxplots of Trivial Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Trivial Partitions")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=trivialPartitions, color=merged)) +
  geom_density() +
  ggtitle("Density Plot of Trivial Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Trivial Partitions")
```

## Non-Trivial Partitions X Trivial Partitions
```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=trivialPartitions)) +
  geom_jitter(position = position_jitter(height = 0, width = 0.3), alpha=0.5, size=3) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Jitter Plot of Non-Trivial Partitions X Trivial Partitions (only width is jittered)") +
  xlab("Non-Trivial Partitions") +
  ylab("Trivial Partitions")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=trivialPartitions, color=merged, shape=merged)) +
  geom_jitter(position = position_jitter(height = 0.1, width = 0.3), alpha=1.0, size=3) +
  ggtitle("Jitter Plot of Non-Trivial Partitions X Trivial Partitions ") +
  xlab("Non-Trivial Partitions") +
  ylab("Trivial Partitions")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=trivialPartitions, color=merged, shape=merged)) +
  geom_jitter(position = position_jitter(height = 0.1, width = 0.3), alpha=1.0, size=3) +
  xlim(0, 5) +
  ylim(0, 20) +
  ggtitle("Jitter Plot of Non-Trivial Partitions X Trivial Partitions (zoomed)") +
  xlab("Non-Trivial Partitions") +
  ylab("Trivial Partitions")
```

## Total Partitions
```{r, echo=FALSE}
ggplot(summ, aes(x=totalPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=1) +
  facet_wrap(~merged, nrow=2) +
  ggtitle("Histogram of Total Partitions in a Pull Request") +
  xlab("Total Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=totalPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_dodge(), col="black", binwidth=1) +
  ggtitle("Histogram of Total Partitions in a Pull Request (dodge)") +
  xlab("Total Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=totalPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_stack(), col="black", binwidth=1) +
  ggtitle("Histogram of Total Partitions in a Pull Request (stack)") +
  xlab("Total Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=totalPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=1) +
  ggtitle("Histogram of Total Partitions in a Pull Request (fill)") +
  xlab("Total Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=merged, y=totalPartitions)) + 
  geom_boxplot() +
  ggtitle("Boxplots of Total Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Total Partitions")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=totalPartitions, color=merged)) +
  geom_density() +
  ggtitle("Density Plot of Total Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Total Partitions")
```

## Ratio of Diff-regions in Non-Trivial Partitions (RDN)
```{r, echo=FALSE}
ggplot(summ, aes(x=rdn, y=0.1*..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=0.1) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Histogram of Ratio of Diff-regions in Non-Trivial Partitions (RDN)") +
  xlab("RDN") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=merged, y=rdn)) +
  geom_boxplot() +
  ggtitle("Boxplot of Ratio of Diff-regions in Non-Trivial Partitions (RDN)") +
  xlab("Merged") +
  ylab("RDN")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=rdn, color=merged)) +
  geom_density() +
  ggtitle("Density Plot of Ratio of Diff-regions in Non-Trivial Partitions (RDN)") +
  xlab("Merged") +
  ylab("RDN")
```

## Ratio of Diff-regions in Trivial Partitions (RDT)
```{r, echo=FALSE}
ggplot(summ, aes(x=rdt, y=0.1*..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=0.1) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Histogram of Ratio of Diff-regions in Trivial Partitions (RDT)") +
  xlab("RDT") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=merged, y=rdt)) +
  geom_boxplot() +
  ggtitle("Boxplot of Ratio of Diff-regions in Trivial Partitions (RDT)") +
  xlab("Merged") +
  ylab("RDT")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=rdt, color=merged)) +
  geom_density() +
  ggtitle("Density Plot of Ratio of Diff-regions in Trivial Partitions (RDT)") +
  xlab("Merged") +
  ylab("RDT")
```

## Diff-regions
```{r, echo=FALSE}
ggplot(summ, aes(x=diffs, y=3*..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=3) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Histogram of Diff-regions") +
  xlab("Diff-regions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged") +
  xlim(0, 100)
```

```{r, echo=FALSE}
ggplot(summ, aes(x=merged, y=diffs)) +
  geom_boxplot() +
  ggtitle("Boxplot of Diff-regions") +
  xlab("Merged") +
  ylab("Diff-regions")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=diffs, color=merged)) +
  geom_density() +
  ggtitle("Density Plot of Diff-regions") +
  xlab("Merged") +
  ylab("Diff-regions")
```

# Conclusions

TODO: Update this. Graphically, there seems to be a a small difference between the distributions.

We did not observe a relationship between the number of partitions detected by our implementation of ClusterChanges and whether the pull request was accepted. However, it is possible that the sample size was too small to detect such a relationship.

# References
