---
title: "Analysis of sample of 513 pull requests"
csl: "ieee.csl"
bibliography: "mergedprs-analysis-2.bib"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

\newpage

```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(dplyr)
library(ggplot2)
library(grid)
library(scales)
library(pander)
```

```{r, echo=FALSE, eval=FALSE}
summ <- read.csv("data/allSummary.csv.gz")
set.seed(1334532099)
summ <- sample_n(summ, 513)
write.csv(summ, "mergedprs-analysis-sample-2.csv")
```

```{r, echo=FALSE}
summ <- read.csv("mergedprs-analysis-sample-2.csv")

# Remove pull requests without diffs
summ <- filter(summ, diffs >= 1)
# Remove open pull requests
summ <- filter(summ, merged == "true" | merged == "false")

pullRequests <- select(summ, projectName, pullRequestId)
partitions <- read.csv("data/allPartitions.csv.gz")
partitions <- partitions %>%
  semi_join(summ, by=c("projectName", "pullRequestId"))

# Adds diffsInNonTrivialPartitions and RDN column to summ
diffsInNonTrivialPartitions <- pullRequests %>%
  left_join(filter(partitions, isTrivial == "false"), by=c("projectName", "pullRequestId")) %>%
  group_by(projectName, pullRequestId) %>%
  summarise(diffsInNonTrivialPartitions = sum(!is.na(isTrivial)))
summ <- summ %>%
  inner_join(diffsInNonTrivialPartitions, by=c("projectName", "pullRequestId")) %>%
  mutate(rdn = diffsInNonTrivialPartitions / diffs)

# Adds diffsInTrivialPartitions and RDN column to summ
summ <- summ %>%
  mutate(diffsInTrivialPartitions = diffs - diffsInNonTrivialPartitions) %>%
  mutate(rdt = diffsInTrivialPartitions / diffs)
```

# Research Question

* RQ1: Can we predict whether a pull request is merged (accepted) based on the number of partitions returned by JClusterChanges?

Intuitively, we expect to observe an inverse correlation between the number of non-trivial partitions and the probability of the pull request being merged. That is, we expect that pull requests with multiple non-trivial partitions will have a low acceptance rate because they likely contain independent modifications and are consequently hard to understand and poorly organized.

# Dataset

We manually inspected 513 pull requests selected at random from the most popular projects in GitHub and, for each of them, we determined: 

* if it was merged (accepted);
* if its status on GitHub is set to "merged"";
* the cause for rejection if it was not merged.

This dataset can be downloaded at: https://github.com/victorclf/ccjava-analysis/blob/master/mergedprs-analysis-sample-2.csv

For this analysis, we discarded open pull requests and pull requests without any diff-regions and ended up with `r count(summ)` closed pull requests for the analysis. Some pull requests do not have any diff-regions because ccjava does not consider code deletions and diff-regions which contain only comments, import statements, package declarations, blank characters and empty lines.

```{r, echo=FALSE}
numPrs <- count(summ)$n
numMergedPrs <- count(filter(summ, merged == "true"))$n
numNonMergedPrs <- count(filter(summ, merged == "false"))$n
```

| Merged  |  Count  |  Proportion  |
|:----:|:----:|:-----:|
|  Yes   |  `r numMergedPrs`   |   `r percent(numMergedPrs / numPrs)`   |
|  No    |  `r numNonMergedPrs` |   `r percent(numNonMergedPrs / numPrs)`   |

Table: Summary of the dataset.

```{r, echo=FALSE}
ggplot(summ, aes(x=projectName, y=..count.., fill=merged)) +
  geom_bar(position = position_stack(), col="black") +
  scale_x_discrete(labels = abbreviate) +
  ggtitle("Histogram of Merged Pull Requests per Project") +
  xlab("Project Name") +
  ylab("Pull Requests") +
  labs(fill = "Merged")
```

# RQ1: Can we predict whether a pull request is merged (accepted) based on the number of partitions returned by ccjava?

## Outlier Removal

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=..density..)) +
  geom_histogram(position = position_identity(), col="black", binwidth=1) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request") +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=trivialPartitions, y=..density..)) +
  geom_histogram(position = position_identity(), col="black", binwidth=1) +
  ggtitle("Histogram of Trivial Partitions in a Pull Request") +
  xlab("Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

In the dataset, there is an [outlier](https://github.com/netty/netty/pull/664) with 46 non-trivial partitions and 394 trivial partitions. This pull request consists of a refactoring where the return types of several methods were changed. Due to the limitations of ClusterChanges, a lot of tiny partitions were generated for this pull request and the results are not representative of the tool. Indeed, the pull request with the second most non-trivial partitions has 9 of them and the pull request with the second most trivial partitions has 73 of them. In order to perform regression analysis and to better visualize data, we have removed this outlier from the analysis.

```{r, echo=FALSE}
summ <- filter(summ, nonTrivialPartitions < 46)
```

## Non-Trivial Partitions

### Visual Analysis

```{r, echo=FALSE, eval=FALSE}
count(filter(summ, nonTrivialPartitions == 0, merged == "true")) / count(filter(summ, merged == "true"))
```

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=1) +
  xlim(c(0, 15)) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request") +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_stack(), col="black", binwidth=1) +
  xlim(c(0, 15)) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request (stack)") +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=1) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request (fill)") +
  xlim(c(0, 15)) +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=3*..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=3) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request (fill, binwidth=3)") +
  xlim(c(0, 15)) +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(summ, aes(x=merged, y=nonTrivialPartitions)) +
  geom_boxplot() +
  ylim(c(0, 15)) +
  ggtitle("Boxplot of Non-Trivial Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Non-Trivial Partitions")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, color=merged)) +
  geom_density() +
  xlim(c(0, 10)) +
  ggtitle("Density Plot of Non-Trivial Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Non-Trivial Partitions")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, color=merged)) +
  stat_ecdf() +
  ggtitle("Distribution Function of Non-Trivial Partitions") +
  xlab("Non-Trivial Partitions") +
  ylab("F(x)")
```

The graphs above show that merged pull requests tend to have fewer non-trivial partitions than rejected ones. This difference becomes increasingly noticeable starting from pull requests with 3 non-trivial partitions which amount to `r count(filter(summ, nonTrivialPartitions >= 3))` pull requests of the `r numPrs` in this dataset.

```{r, echo=FALSE, fig.width=7.5, fig.height=11}
ggplot(summ, aes(x=nonTrivialPartitions, y=1*..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=1) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request (fill)") +
  xlim(c(0, 11)) +
  facet_wrap(~projectName, nrow = 5, ncol = 2) +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE, fig.width=7.5, fig.height=11}
ggplot(summ, aes(x=nonTrivialPartitions, y=3*..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=3) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request (fill, binwidth=3)") +
  xlim(c(0, 11)) +
  facet_wrap(~projectName, nrow = 5, ncol = 2) +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE, fig.width=7.5, fig.height=11}
ggplot(summ, aes(x=nonTrivialPartitions, y=4*..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=4) +
  ggtitle("Histogram of Non-Trivial Partitions in a Pull Request (fill, binwidth=4)") +
  xlim(c(0, 11)) +
  facet_wrap(~projectName, nrow = 5, ncol = 2) +
  xlab("Non-Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

In general, the histograms for each of the projects above also point to an inverse relationship between non-trivial partitions and the probability of a pull request being merged. It seems that the relationship also applies for each of the individual projects.

### Logistic Regression\label{subsec:ntpLogReg}

```{r, echo=FALSE}
ntpGlm <- glm(merged ~ nonTrivialPartitions, family=binomial(link = "logit"), data=summ)
summary(ntpGlm)
ntpGlmLikeRatioP <- with(ntpGlm, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))
```

Logistic regression allows us to evaluate if there is an association between the number of non-trivial partitions and the acceptance of a pull request and also to predict whether a pull request will be accepted if the resulting model fits well.

Our null hypothesis H0 for this test is that the probability of a pull request being merged is not associated with the number of non-trivial partitions and we use a significance level of 5%. The alternative hypothesis H1 is that there is in fact a relationship between the two variables.

The p-value from the z-test for the coefficient of nonTrivialPartitions is lower than 0.05 and therefore we do not reject its corresponding null hypothesis that the coefficient is equal to 0.

Moreover, using the likelihood ratio test to evaluate the goodness of fit of the model by comparing it with the null model, we obtained a p-value of `r ntpGlmLikeRatioP`. Thus, we reject the null hypothesis H0 and accept H1 at a significance level of 5%.

The equation for this regression model is the following:

$Y/1-Y = exp(`r txntpGlm$coefficients[1]` + `r txntpGlm$coefficients[2]` * NTP + `r txntpGlm$coefficients[3]` * TP + `r txntpGlm$coefficients[4]` * NTP * TP)$

\newpage

```{r, echo=FALSE}
pander(t(tabm1(0:10, 0:20)), style="rmarkdown", emphasize.rownames=FALSE, split.tables=120)
```

The table above shows the values 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
summM1 <- select(as.data.frame(tabm1(0:10, 0:20)), trivialPartitions = Var2, nonTrivialPartitions = Var1, odds = Freq)

ggplot(summM1, aes(x=nonTrivialPartitions, y=trivialPartitions)) +
  geom_tile(aes(fill=odds)) +
  scale_x_discrete() +
  scale_y_discrete() +
  xlab("Non-Trivial Partitions") +
  ylab("Trivial Partitions") +
  labs(fill = "Odds for merge")
```


## Trivial Partitions

### Visual Analysis

```{r, echo=FALSE}
ggplot(summ, aes(x=trivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=1) +
  xlim(c(0, 32)) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Histogram of Trivial Partitions in a Pull Request") +
  xlab("Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=trivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_stack(), col="black", binwidth=1) +
  xlim(c(0, 32)) +
  ggtitle("Histogram of Trivial Partitions in a Pull Request (stack)") +
  xlab("Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=trivialPartitions, y=1*..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=1) +
  xlim(c(0, 32)) +
  ggtitle("Histogram of Trivial Partitions in a Pull Request (fill)") +
  xlab("Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=trivialPartitions, y=9*..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=9) +
  xlim(c(0, 32)) +
  ggtitle("Histogram of Trivial Partitions in a Pull Request (fill, binwidth=9)") +
  xlab("Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(summ, aes(x=merged, y=trivialPartitions)) + 
  geom_boxplot() +
  ylim(c(0,32)) +
  ggtitle("Boxplots of Trivial Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Trivial Partitions")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(summ, aes(x=trivialPartitions, color=merged)) +
  geom_density() +
  xlim(c(0, 32)) +
  ggtitle("Density Plot of Trivial Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Trivial Partitions")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(summ, aes(x=trivialPartitions, color=merged)) +
  stat_ecdf() +
  ggtitle("Distribution Function of Trivial Partitions") +
  xlab("Trivial Partitions") +
  ylab("F(x)")
```

Starting from 9 trivial partitions, rejected pull requests become increasingly more common than merged ones. This suggests that there is an inverse relationship between the two variables.

```{r, echo=FALSE, fig.width=7.5, fig.height=11}
ggplot(summ, aes(x=trivialPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=1) +
  ggtitle("Histogram of Trivial Partitions in a Pull Request (fill)") +
  xlim(c(0, 20)) +
  facet_wrap(~projectName, nrow = 5, ncol = 2) +
  xlab("Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE, fig.width=7.5, fig.height=11}
ggplot(summ, aes(x=trivialPartitions, y=9*..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=9) +
  ggtitle("Histogram of Trivial Partitions in a Pull Request (fill, binwidth=9)") +
  xlim(c(0, 20)) +
  facet_wrap(~projectName, nrow = 5, ncol = 2) +
  xlab("Trivial Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

Most of the histograms above, which consider the data of each project individually, provide further evidence to our observation that pull requests with at least 9 trivial partitions tend to be rejected more often than pull requests with less than 9 trivial partitions.

### Logistic Regression

```{r, echo=FALSE}
tpGlm <- glm(merged ~ trivialPartitions, family=binomial(link = "logit"), data=summ)
summary(tpGlm)
tpGlmLikeRatioP <- with(tpGlm, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))
```

Our null hypothesis H0 for this test is that the probability of a pull request being merged is not associated with the number of trivial partitions and we use a significance level of 5%.

The p-value from the z-test for the coefficient of trivialPartitions is higher than 0.05 and therefore we do not reject its corresponding null hypothesis that the coefficient is equal to 0.

Moreover, using the likelihood ratio test to evaluate the goodness of fit of the model by comparing it with the null model, we obtained a p-value of `r tpGlmLikeRatioP`. Thus, *there is no evidence to reject the null hypothesis H0* at a significance level of 5%.

## Non-Trivial Partitions X Trivial Partitions

### Visual Analysis
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7.5, fig.height=11}
ggplot(summ, aes(x=nonTrivialPartitions, y=trivialPartitions)) +
  geom_jitter(position = position_jitter(height = 0, width = 0.3), alpha=0.3, size=3) +
  xlim(0, 10) +
  ylim(0, 75) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Jitter Plot of Non-Trivial Partitions X Trivial Partitions (only width is jittered)") +
  xlab("Non-Trivial Partitions") +
  ylab("Trivial Partitions")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=trivialPartitions, color=merged, shape=merged)) +
  geom_jitter(position = position_jitter(height = 0.1, width = 0.3), alpha=1.0, size=3) +
  xlim(0, 10) +
  ylim(0, 32) +
  ggtitle("Jitter Plot of Non-Trivial Partitions X Trivial Partitions ") +
  xlab("Non-Trivial Partitions") +
  ylab("Trivial Partitions")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(summ, aes(x=nonTrivialPartitions, y=trivialPartitions, color=merged, shape=merged)) +
  geom_jitter(position = position_jitter(height = 0.1, width = 0.3), alpha=1.0, size=3) +
  xlim(0, 5) +
  ylim(0, 20) +
  ggtitle("Jitter Plot of Non-Trivial Partitions X Trivial Partitions (zoomed)") +
  xlab("Non-Trivial Partitions") +
  ylab("Trivial Partitions")
```

The scatter plot of rejected pull requests looks more disperse than the scatter plot of merged pull requests. Rejected pull requests seem to have more partitions than merged pull requests.

### Logistic Regression

```{r, echo=FALSE}
txntpGlm <- glm(merged ~ nonTrivialPartitions * trivialPartitions, family=binomial(link = "logit"), data=summ)
summary(txntpGlm)
txntpGlmLikeRatioP <- with(txntpGlm, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))
txntpVSntpGlmLikeRatioP <- pchisq(ntpGlm$deviance - txntpGlm$deviance, ntpGlm$df.residual - txntpGlm$df.residual, lower.tail = FALSE)
```

```{r, echo=FALSE}
m1 <- function(ntp, tp) {
  return (exp(txntpGlm$coefficients[1] + txntpGlm$coefficients[2] * ntp + txntpGlm$coefficients[3] * tp + txntpGlm$coefficients[4] * ntp * tp))
}

tabm1 <- function(ntpSeq, tpSeq) {
  r <- matrix(nrow=length(ntpSeq), ncol=length(tpSeq))
  for (ntpIndex in seq(along.with=ntpSeq)) {
    for (tpIndex in seq(along.with=tpSeq)) {
      r[ntpIndex, tpIndex] <- m1(ntpSeq[ntpIndex], tpSeq[tpIndex])
    }
  }
  s <- as.table(r)
  rownames(s) <- ntpSeq
  colnames(s) <- tpSeq
  return(s)
}
```

Our null hypothesis H0 for this test is that the probability of a pull request being merged is not associated with the number of non-trivial partitions and the number of trivial partitions and we use a significance level of 5%.

The p-value from the z-test for the nonTrivialPartitions coefficient is `r summary(txntpGlm)$coefficients[2,4]` which is lower than the significance level of 0.05. Therefore, we reject the corresponding null hypotheses that this coefficient is equal to 0.

Furthermore, using the likelihood ratio test to evaluate the goodness of fit of the model by comparing it with the null model, we obtained a p-value of `r txntpGlmLikeRatioP`. Thus, there is evidence to reject the null hypothesis H0 at a significance level of 5%.

Nonetheless, since the only significant independent variable in this model is the number of non-trivial partitions, the simple logistic regression model presented in section \ref{subsec:ntpLogReg} might be preferrable. We used a likelihood ratio test to compare this model with the simpler one which uses just non-trivial partitions as input and obtained a p-value of `r txntpVSntpGlmLikeRatioP`. This means that this model is not better than the simpler one.

## Total Partitions
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(summ, aes(x=totalPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=1) +
  xlim(c(0, 40)) +
  facet_wrap(~merged, nrow=2) +
  ggtitle("Histogram of Total Partitions in a Pull Request") +
  xlab("Total Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(summ, aes(x=totalPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_stack(), col="black", binwidth=1) +
  xlim(c(0, 40)) +
  ggtitle("Histogram of Total Partitions in a Pull Request (stack)") +
  xlab("Total Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(summ, aes(x=totalPartitions, y=..density.., fill=merged)) +
  geom_histogram(position = position_fill(), col="black", binwidth=1) +
  xlim(c(0, 40)) +
  ggtitle("Histogram of Total Partitions in a Pull Request (fill)") +
  xlab("Total Partitions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(summ, aes(x=merged, y=totalPartitions)) + 
  geom_boxplot() +
  ylim(c(0, 40)) +
  ggtitle("Boxplots of Total Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Total Partitions")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(summ, aes(x=totalPartitions, color=merged)) +
  geom_density() +
  xlim(c(0, 40)) +
  ggtitle("Density Plot of Total Partitions in a Pull Request") +
  xlab("Merged") +
  ylab("Total Partitions")
```

## Ratio of Diff-regions in Non-Trivial Partitions (RDN)
```{r, echo=FALSE}
ggplot(summ, aes(x=rdn, y=0.1*..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=0.1) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Histogram of Ratio of Diff-regions in Non-Trivial Partitions (RDN)") +
  xlab("RDN") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=merged, y=rdn)) +
  geom_boxplot() +
  ggtitle("Boxplot of Ratio of Diff-regions in Non-Trivial Partitions (RDN)") +
  xlab("Merged") +
  ylab("RDN")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=rdn, color=merged)) +
  geom_density() +
  ggtitle("Density Plot of Ratio of Diff-regions in Non-Trivial Partitions (RDN)") +
  xlab("Merged") +
  ylab("RDN")
```

## Ratio of Diff-regions in Trivial Partitions (RDT)
```{r, echo=FALSE}
ggplot(summ, aes(x=rdt, y=0.1*..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=0.1) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Histogram of Ratio of Diff-regions in Trivial Partitions (RDT)") +
  xlab("RDT") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=merged, y=rdt)) +
  geom_boxplot() +
  ggtitle("Boxplot of Ratio of Diff-regions in Trivial Partitions (RDT)") +
  xlab("Merged") +
  ylab("RDT")
```

```{r, echo=FALSE}
ggplot(summ, aes(x=rdt, color=merged)) +
  geom_density() +
  ggtitle("Density Plot of Ratio of Diff-regions in Trivial Partitions (RDT)") +
  xlab("Merged") +
  ylab("RDT")
```

## Diff-regions
```{r, echo=FALSE}
ggplot(summ, aes(x=diffs, y=3*..density.., fill=merged)) +
  geom_histogram(position = position_identity(), col="black", binwidth=3) +
  facet_wrap(~merged, nrow = 2) +
  ggtitle("Histogram of Diff-regions") +
  xlab("Diff-regions") +
  ylab("Proportion (in-group) of Pull Requests") +
  labs(fill = "Merged") +
  xlim(0, 100)
```

```{r, echo=FALSE}
ggplot(summ, aes(x=merged, y=diffs)) +
  geom_boxplot() +
  ggtitle("Boxplot of Diff-regions") +
  xlab("Merged") +
  ylab("Diff-regions")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(summ, aes(x=diffs, color=merged)) +
  geom_density() +
  xlim(c(0, 200)) +
  ggtitle("Density Plot of Diff-regions (zoomed)") +
  xlab("Merged") +
  ylab("Diff-regions")
```

# Conclusions

**TODO**

# References
